\sysfull

### 2018-08-02 paper/oopsla18/background.tex
restructure the paper directory

% \begin{wrapfigure}{t!}{0.5\textwidth}
\begin{figure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example}
		\caption{Simplified C code snippet of a CRC calculation from~\cite{hicks_mibench2_2016}: per-byte message division by a polynomial; \texttt{NV} denotes non-volatile variable declaration.}\label{fig:crc_example}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example_war}
		\caption{Execution steps of the loop body in the snippet above: non-volatile checkpointing did not guarantee data consistency as data has been manipulated (line 9) with stale reminder (line 3)}\label{fig:crc_example_war}
	\end{subfigure}
	\caption{Code example demonstrating checkpointing gives rise to data inconsistency.}\label{fig:code_demo_incosistency}
% \end{wrapfigure}
\end{figure}

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + Stack + WAR NV variables \\%used in task\\
		Chain~\cite{chain}	& PC + NV variables used in task\\
		Alpaca~\cite{alpaca}	& PC + WAR NV variables used in task\\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
		\hline
	\end{tabular}
	\caption{Non-volatile memory access for data consistency; \emph{PC}: program counter, \emph{WAR variables}: variables involved in Write after Read (WAR) dependences, \emph{NV}: non-volatile.}
	\label{table:chechpoint_comparison}
\end{table}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example}
		\caption{Simplified C code snippet of a CRC calculation from~\cite{hicks_mibench2_2016}: per-byte message division by a polynomial; \texttt{NV} denotes non-volatile variable declaration.}\label{fig:crc_example}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example_war}
		\caption{Execution steps of the loop body in the snippet above: non-volatile checkpointing did not guarantee data consistency as data has been manipulated (line 9) with stale reminder (line 3)}\label{fig:crc_example_war}
	\end{subfigure}
	\caption{Code example demonstrating checkpointing gives rise to data inconsistency.}\label{fig:code_demo_incosistency}
\end{wrapfigure}
%\end{figure}

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + Stack + WAR NV variables used in task\\
		Chain~\cite{chain}	& PC + NV variables used in task\\
		Alpaca~\cite{alpaca}	& PC + WAR NV variables used in task\\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
		\hline
	\end{tabular}
	\caption{Non-volatile memory access for data consistency; \emph{PC}: program counter, \emph{WAR variables}: variables involved in Write after Read (WAR) dependences, \emph{NV}: non-volatile.}
	\label{table:chechpoint_comparison}
\end{table}
